Something with Objects and Names

### 2019-12-05 papers/ACL2020/experiments.tex
new table: results for high and low agreement entry level names

>>>>

\begin{table*}[t]
\centering
	\small
\begin{tabular}{lrrr||rrr}
\toprule
&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
\midrule
       FRCNN--VG1600\_VG &      0.95 &          0.02 &            0.03 &     0.64 &         0.24 &           0.12 \\
        FRCNN--MN442\_VG &      0.90 &          0.02 &            0.09 &     0.61 &         0.24 &           0.15 \\
         \midrule \midrule
 FRCNN--VG1600--VGMN\_MN &      0.95 &          0.01 &            0.04 &     0.73 &         0.16 &           0.11 \\
 \midrule 
     ResNet101--VGMN\_VG &      0.88 &          0.02 &            0.10 &     0.49 &         0.24 &           0.28 \\
     ResNet101--VGMN\_MN &      0.90 &          0.02 &            0.09 &     0.57 &         0.19 &           0.24 \\
    ResNet101--MN442\_MN &      0.90 &          0.01 &            0.09 &     0.58 &         0.20 &           0.22 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} for objects with a high agreement entry-level name and less agreement entry-level names. \label{tab:errors_agreement}}
\end{table*}
